---
title: "Covid-19 packages"
author: "M. Rolland"
date: "17/07/2020"
output: 
  html_document:
    number_sections: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(pkgsearch)
library(kableExtra)
```

This document lists all major covid-19 and epidemiology packages.

To do:

* checkout https://rviews.rstudio.com/2020/08/10/us-covid-19-forecasts/  

# Covid 19 specific

## Automated search

```{r echo = TRUE}
# list epidemiology packages
cov19 <- pkg_search(query="covid covid19 coronavirus",size=200)
```

```{r}
# filter those with score > 10 and > 500 downloads last month
cov19 <- as_tibble(cov19) %>% 
  filter(score >= 10) %>% 
  select(package,title, downloads_last_month) %>% 
  arrange(-downloads_last_month)

cov19 %>%
  kable(caption = "Covid 19 packages") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## Manual search

Mainly from [Top 100 R resources on Novel COVID-19 Coronavirus - 12-03-2020](https://www.statsandr.com/blog/top-r-resources-on-covid-19-coronavirus/)

* [{nCov2019}](https://github.com/GuangchuangYu/nCov2019): access to epidemiological data on the Coronavirus outbreak. Gives real-time statistics, includes historical data and a Shiny app. ([vignette](https://guangchuangyu.github.io/nCov2019/))
* [{coronavirus}](https://github.com/RamiKrispin/coronavirus): provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic
* [{tidycovid19}](https://github.com/joachim-gassen/tidycovid19): download, tidy and visualize Covid-19 related data (including data on governmental measures) directly from authoritative sources
* [{covdata}](https://kjhealy.github.io/covdata/): provides COVID-19 case data from multiple sources
* [{covid19italy}](https://github.com/Covid19R/covid19italy): provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) pandemic outbreak in Italy ([vignette](https://covid19r.github.io/covid19italy/articles/intro.html))
* [{COVID19}](https://covid19datahub.io/): provide the research community with a unified data hub 
* [{COVOID}](https://cbdrh.github.io/covoidance/): modelling COVID-19 and other infectious diseases using deterministic compartmental models (DCMs)
* [{cdccovidview}](https://cinc.rud.is/web/packages/cdccovidview/index.html): used to work with the U.S. CDC’s New COVID-19 Trackers: [COVIDView](https://www.cdc.gov/coronavirus/2019-ncov/covid-data/covidview/index.html) and [COVID-NET](https://gis.cdc.gov/grasp/COVIDNet/COVID19_3.html)

# Epidemiology

## Automated search

```{r echo = TRUE}
# list epidemiology packages
epi <- pkg_search(query="epidemiology epidemic",size=200)
```


```{r}
# filter those with score > 10 and > 500 downloads last month
epi <- as_tibble(epi) %>% 
  filter(score >= 10) %>% 
  select(package,title,downloads_last_month) %>% 
  arrange(-downloads_last_month)

epi %>%
  kable(caption = "Epi packages") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



# Interesting links

[Top 100 R resources on Novel COVID-19 Coronavirus - 12-03-2020](https://www.statsandr.com/blog/top-r-resources-on-covid-19-coronavirus/)  
[An R View into Epidemiology - 19-05-2020](https://www.r-bloggers.com/an-r-view-into-epidemiology/)


