---
title: "RECON COVID-19 challenge"
subtitle: "Project log"
date: "last modified `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(DiagrammeR)
library(pander)
```

## Useful links

* [Project repo](https://github.com/mjrolland/covid-19-challenge)  
* [Link to Trello](https://trello.com/b/PQch7ney/covid19-challenge)  
* [Link to Slack](https://app.slack.com/client/T2SFJJQRL/G016PGWRPAA/thread/C2SFJJV8E-1594388640.056600)  
* [Documents created by Matthieu](https://mjrolland.github.io/covid-19-challenge/docs/document_list.html)  

## Time line

```{r out.width = "100%", fig.height = 3}
DiagrammeR::mermaid("
gantt
dateFormat  YYYY-MM-DD
title RECON COVID-19 CHALLENGE TIMELINE

section Milestones
1. setup                      :done,          overall_1,   2020-07-10, 1d
2. early stage assessment     :active         overall_2,  after overall_1, 2020-08-07   
3. initial release            :               overall_3,  2020-08-08, 2020-08-30
4. mid-stage assessment       :               overall_4,  after overall_3, 2020-09-27
5. second release             :               overall_5,  after overall_4, 2020-10-10
6. task view epidemics        :               overall_6,  after overall_5, 2020-10-25
7. final assessment           :               overall_7,  after overall_6, 2020-11-27

section Matthieu

section Benjamin
")
```

## Log

2020-07-10: [Launch meeting](meeting_notes/2020-07-10_launch_meeting.html)  
2020-07-17: [Meeting - Ben + Matt](meeting_notes/2020-07-17_meeting.html)  
2020-07-24: [Meeting - Ben + Matt](meeting_notes/2020-07-24_meeting.html)  
2020-07-27: [Meeting - Ben + Matt](meeting_notes/2020-07-27_meeting.html)  
2020-07-30: [Meeting - Ben + Matt](meeting_notes/2020-07-30_meeting_1.html)  
2020-07-30: [Meeting - Thibaut + Matt](meeting_notes/2020-07-30_meeting_2.html)  
2020-08-07: [Server needs](server_needs.html)  
2020-08-07: [Meeting - Ben + Matt](meeting_notes/2020-08-07_meeting.html)  
2020-08-17: [Meeting - Ben + Matt](meeting_notes/2020-08-17_meeting.html)  
2020-08-21: [Meeting - Ben + Matt](meeting_notes/2020-08-21_meeting.html)  
2020-08-24: [Early assessment meeting](meeting_notes/2020-08-24_early_assessment_meeting.html)   
2020-08-28: [DSCC19 conf - link to talk](https://www.youtube.com/watch?v=E39BMCJsbx4&list=PL41aTiRjzS9sG2wtz6qusI4ZD2CDMV04O&index=8&t=0s)  
2020-09-04: Meeting - Ben + Matt, no progress due to DSCC19  
2020-09-11: [Meeting - Ben + Matt](meeting_notes/2020-09-11_meeting.html)  
2020-09-21: [Meeting - Ben + Matt](meeting_notes/2020-09-21_meeting.html)  
2020-09-25: [Meeting - Ben + Matt](meeting_notes/2020-09-25_meeting.html)  
2020-09-28: [Meeting - Ben + Matt](meeting_notes/2020-09-28_meeting.html)  
2020-10-02: Recon general assembly   
2020-10-09: [Meeting - Thibaut + Matt](meeting_notes/2020-10-09_meeting_b.html)  
2020-10-09: [Meeting - Ben + Matt](meeting_notes/2020-10-09_meeting.html)  
